---
title: "CIS 600 Final Project - Digit Recognition"
author: Gafei, Greg Shin, Ashraf Elnashar
date: Nov. 11th, 2019
output: html_document
theme: cerulean
---

## Introduction
The ultimate goal in creating a stock portfolio is to gather a group of stocks that will increase in value overtime. However, it is often difficult to pick which stocks to invest in from all the ones that are available.Therefore, we intend to explore the use of clustering analysis in identifying groups of similarly performingstocks.

## Goal
To use clustering techniques with historical stock prices to group different stocks together, in orderto form an investment strategy.

## Load Libraries
  
```{r setup}
#Function that loads libraries
EnsurePackage <- function(x) {
  x <- as.character(x)
  if (!require(x,character.only = T))
    install.packages(x,repos = "https://cran.rstudio.com/")
  require(x,character.only = T)
}

EnsurePackage("caret") # set of functions that attempt to streamline the process for creating predictive models
EnsurePackage("rpart") #Recursive Partitioning And Regression Trees
EnsurePackage("DMwR") #Smote
EnsurePackage("rattle") #graphical user interface to many other R packages that provide functionality for data mining
EnsurePackage("tidyverse") #Manipulating dataset
EnsurePackage("ggplot2")
EnsurePackage("readr")
EnsurePackage("dplyr") #selecting data
EnsurePackage("magrittr") #using pipe operators
EnsurePackage("corrplot")
EnsurePackage("knitr")
EnsurePackage("dplyr") #selecting data
EnsurePackage("sm")
EnsurePackage("gmodels")
EnsurePackage("rpart") #Recursive Partitioning and Regression Trees
EnsurePackage("rpart.plot")
EnsurePackage("plotly")
EnsurePackage("e1071") #deals with Probability group theory functions
EnsurePackage("RColorBrewer")  #coloring of graphs
EnsurePackage("plotly")
```

## Load Data

```{r, echo = TRUE}

  path <- 'stock_prices_latest_Simplified.csv'
  dataSetReader <-read.csv(path)
  
  #summary of Stock Prices.
  str(dataSetReader)

  #Head.
  head(dataSetReader)

  #Tail.
  tail(dataSetReader)
```

```{r, echo = FALSE}
child_docs <- c("child/1_DataPreprocessing.Rmd","child/3_CreateTrainTestSet.Rmd")
```

```{r child = child_docs}
```
